\documentclass[10pt]{article}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\usepackage[margin=1in]{geometry}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
	\begin{flushleft}
		\LARGE\textbf{\@title}
		
		\normalsize\@author
	\end{flushleft}\egroup
}
\makeatother
\title{Diego Gutierrez}
\date{}
\author{%
	PO Box 187, Rockport Maine 04856\\
	\textbf{Phone:} 207-317-3663, \textbf{Email:} dgutierrez1287@gmail.com\\
	\textbf{Github:} www.github.com/dgutierrez1287\\
	\textbf{DockerHub:} https://hub.docker.com/dgutierrez1287
}

\pagestyle{empty} % disables page numbers
\begin{document}
\maketitle
\thispagestyle{empty} % single page disable page number
\noindent\Large\textbf{Summary:}\\
\normalsize Performance-driven and strategic professional with extensive experience spearheading engineering projects, 
automating workflows, and boosting software delivery efficiency for diverse tech companies. Proficient in implementing transformative initiatives, 
streamlining business processes, and supervising product development from conception to commercialization. Excel in leading cloud infrastructure 
integrations and continuous deployment strategies, enhancing customer experience, and administering coaching and mentorship to drive business 
objectives while promoting change management.
\\
\\
\noindent\Large\textbf{Experience:}\\
\normalsize
\textbf{Lead DevOps Engineer, Oddball, Inc. \hfill{Febuary 2020 - Present}}\\
\normalsize Architect and execute company's DevOps strategy, leading process of infrastructure implementation and system optimization. 
Utilize innovative methods to foster environment of ongoing improvement, accelerating product delivery process and reducing system downtime.
\begin{itemize}
\small
\item \textbf{Managed and led a team of 6 DevOps engineers}.
\item \textbf{Orchestrated transition from ECS Fargate to Kubernetes,} maximizing system reliability and scalability and slashing operational costs.
\item \textbf{Innovated CI/CD system with Jenkins,} streamlining development process and expediting release process.
\item \textbf{Led DevOps engineers to unprecedented levels of efficiency,} driving innovation in process management and boosting
team productivity. 
\item \textbf{Strategized and implemented NoSQL databases with Development team,} resulting in optimized data management,
efficient data retrieval and lower costs.
\item \textbf{Designed monitoring and alerting system,} hat minimized outages and advanced overall system responsiveness.
\item \textbf{Achieved multiple federal bids,} by presenting compelling DevOps solutions, while increasing project wins.
\item \textbf{Ensured organization's compliance with government regulatory standards,} such as FEDRAMP and HIPPA, fortifying
security standards and mitigating potential risks.
\end{itemize}

\normalsize
\noindent\textbf{Senior Cloud Operations Engineer, O'Reilly Media, Inc. \hfill{November 2018 - Febuary 2020}}\\
\normalsize Oversaw monitoring and optimization of cloud-based systems, utilizing cutting-edge tools to identify and resolve 
performance bottlenecks and potential security vulnerabilities. Collaborated with cross-functional teams to architect and deploy complex 
cloud solutions, ensuring resource utilization and cost efficiency.
\begin{itemize}
\small
\item \textbf{Drove migration from On-Premises to Google Cloud,} enhancing scalability and minimizing infrastructure expenses through Kubernetes and GKE utilization.
\item \textbf{Partnered with development teams to devise CI/CD tools,} facilitating operations across different environments.
\item \textbf{Led secure integration of Jupyter Notebooks with Kubernetes,} elevating data analysis workflows.
\item \textbf{Directed cross-functional teams in continuous improvement of cloud systems and services,} promoting culture of
innovation and excellence.
\end{itemize}

\normalsize
\noindent\textbf{Senior DevOps Engineer, WEX, Inc. \hfill{August 2017 - November 2018}}\\
\normalsize Adopted DevOps best practices within organization, including automation, source code management, integrated build systems, 
and testing frameworks. Monitored industry trends and advancements in DevOps technologies, implementing innovative solutions.
\begin{itemize}
\small
\item \textbf{Executed PCI-compliant system automation strategy,} contributing to organization's robust security posture.
\item \textbf{Revamped mobile team's tools and systems,} fostering dynamic DevOps culture in \textbf{\$1.72B+} financial services enterprise.
\item \textbf{Led creation of company's configuration management processes,} improving IT operation efficiency.
\item \textbf{Collaborated with IT team to architect hybrid on-premises and cloud infrastructure,} setting groundwork for future
enterprise-wide AWS transition.
\item \textbf{Received recognition from CTO} for driving automation and employing best practices
\end{itemize}

\normalsize
\noindent\textbf{Systems Administrator II, IDEXX Laboratories \hfill{October 2014 - August 2017}}\\
\normalsize 
\begin{itemize}
\small
\item \textbf{Supervised migration} of two ASP.NET applications to AWS, slashing operational costs.
\item \textbf{Managed AWS infrastructure,} leading to increase in resource utilization efficiency through automation strategies.
\item \textbf{Coordinated multi-application system's migration into Docker} containers, streamlining deployment processes.
\item \textbf{Created business statistics collection system,} aiding in more data-driven decision-making and strategic planning,
enhancing overall business performance.
\end{itemize}

\normalsize
\noindent\textbf{Systems / Network Administrator, BlueTarp Financial \hfill{July 2012 - October 2014}}\\
\normalsize 
\begin{itemize}
\small
\item \textbf{Devised process automation strategies} that elevated system productivity and saved substantial time and effort.
\item \textbf{Spearheaded migration of existing infrastructure to Puppet,} increasing system stability and reducing recovery times.
\item \textbf{Boosted system effectiveness} by managing Windows and Linux servers, switches, and NetApp SAN storage.
\end{itemize}

\noindent\Large\textbf{Certifications:}\\
\normalsize
AWS Certified Cloud Practitioner | Amazon Web Services (AWS)
\\
\\
\normalsize
\noindent\Large\textbf{Skills:}\\
\normalsize
\textbf{Languages:}
\normalsize Java, C, C{\#}, SQL, Python, Ruby, PowerShell, Groovy, Puppet, Ansible, CSS, Javascript, LaTeX, Go, Bash, Terraform \\
\textbf{Frameworks:}
\normalsize Spring Boot, Spring Security, Liquibase, Hibernate, JPA, Django \\
\textbf{Development Tools:}
\normalsize Maven, Gradle, NPM, Jenkins, Git, Subversion, Docker \\
\textbf{Application Servers:}
\normalsize Apache, Nginx, Tomcat, IIS, JBoss \\
\textbf{Databases:}
\normalsize SQLServer, MySQL, Postgres, MongoDB \\
\textbf{Systems/Networking:}
\normalsize Windows Server, Linux, VMWare and Hyper-V, Windows AD \& DNS, DHCP, Cisco Switches, ASA FireWalls, VLANS and other advanced layer 3 networking, Kubernetes \\
\textbf{Cloud Providers:}
\normalsize Amazon Web Services, Google Cloud
\\
\\
\noindent\Large\textbf{References available upon request}
\end{document}
